---
title: "RAVE Pipeline Markdown Template"
format: html
editor: visual
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
build_pipeline <- raveio::configure_knitr()
# build_pipeline(make_file = "make-power_explorer.R")
.settings <- raveio::load_yaml(file.path(rstudioapi::getActiveProject(), "modules", 'power_explorer', "settings.yaml"))
list2env(as.list(.settings), envir = environment())
```

```{rave check_load_power, language = "R", export = "repository", cue = "always"}
# raveio::pipeline_debug(quick = FALSE)
subject_id <- sprintf("%s/%s", project_name, subject_code)
repository <- raveio::prepare_subject_power(
  subject = subject_id, electrodes = loaded_electrodes, 
  epoch_name = epoch_choice, reference_name = reference_name,
  time_windows = c(epoch_choice__trial_starts, epoch_choice__trial_ends))
repository
```

```{rave check_requested_electrodes, language = "R", export = "requested_electrodes"}
requested_electrodes <- dipsaus::parse_svec(analysis_electrodes, sep=',|;', connect  = ':-')
requested_electrodes <- requested_electrodes[requested_electrodes %in% repository$power$LFP$electrodes]
if(!length(requested_electrodes)){ stop("No electrode selected") }
```

```{rave check_analysis_ranges, language = "R", export = "analysis_ranges_index"}
library(rutabaga)
analysis_ranges_index <- lapply(analysis_ranges, function(x){
  x$frequency <- unlist(x$frequency)
  x$time <- unlist(x$time)
  if(length(x$frequency) == 2){
    if(!any(repository$frequency %within% x$frequency)){
      stop(sprintf("No frequencies available within specified range: %.1f ~ %.1f", x$frequency[[1]], x$frequency[[2]]))
    }
  } else {
    return(NULL)
  }
  if(length(x$time) == 2){
    if(!any(repository$time_points %within% x$time)){
      stop(sprintf("No time-points available within specified range: %.2f ~ %.2f", x$time[1], x$time[2]))
    }
  } else {
    return(NULL)
  }
  
  list(
    Frequency = which(repository$frequency %within% x$frequency),
    Time = which(repository$time_points %within% x$time)
    # Electrode = which(repository$power$LFP$electrodes %in% requested_electrodes)
  )
})
```

```{rave check_condition_groups, language = "R", export = "cond_groups"}
# clean groups
cond_groups <- lapply(seq_along(condition_groups), function(idx){
  g <- condition_groups[[idx]]
  g_cond <- sort(unlist(g$group_conditions))
                   
  Trial_num <- repository$epoch$table$Trial[
    repository$epoch$table$Condition %in% g_cond
  ]
  list(
    name = g$group_name,
    Trial_num = Trial_num,
    group_index = idx,
    has_trials = length(Trial_num) > 0,
    conditions = g_cond
  )
})

has_trials <- vapply(cond_groups, '[[', FALSE, 'has_trials')
if(!has_trials){
  stop("No trial condition selected")
}

```

```{rave calculate_baseline, language = "R", export = "bl_power", cue = "always"}
baseline_along_choices <- c("Per frequency, trial, and electrode", "Across electrode", "Across trial", "Across trial and electrode")
baseline_choice <- which(baseline_along_choices %in% baseline__global_baseline_choice)
units <- list(
  c("Trial", "Frequency", "Electrode"),
  c("Trial", "Frequency"),
  c("Frequency", "Electrode"),
  c("Frequency")
)[[baseline_choice]]

method <- list(`% Change Power` = "percentage", `% Change Amplitude` = "sqrt_percentage", 
        `z-score Power` = "zscore", `z-score Amplitude` = "sqrt_zscore", 
        Decibel = "decibel")[[baseline__unit_of_analysis]]

old_file <- repository$baselined$LFP$.filebase

raveio::power_baseline(
  x = repository,
  baseline_windows = unlist(baseline__windows),
  method = method,
  units = units,
  signal_types = "LFP",
  electrodes = requested_electrodes
)

new_file <- repository$baselined$LFP$.filebase
if(length(old_file) == 1 && !identical(old_file, new_file) && dir.exists(old_file)){
  unlink(old_file)
}

bl_power <- repository$baselined$LFP
```

```{rave collapse_data, language = "R", export = "collapsed_data"}
collapsed_data <- lapply(cond_groups, function(g){
  if(!g$has_trials){ return(g) }
  analysis_idx <- structure(
    lapply(analysis_ranges_index, function(x){
      x$Trial <- g$Trial_num
      x
    }),
    names = sprintf("range_%d", seq_along(analysis_ranges_index))
  )
  g$collasped <- raveio::collapse_power(bl_power, analysis_idx)
  g
})
```

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-power_explorer.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-power_explorer.R")
```

Once the pipeline script `make-power_explorer.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r execute}
Sys.setenv("RAVE_PIPELINE" = normalizePath("."))
raveio::pipeline_run(type = "vanilla")
raveio::pipeline_progress(method = 'details')
```

```{r visualize, echo=FALSE}
Sys.setenv("RAVE_PIPELINE" = normalizePath("."))
raveio::pipeline_visualize()
```
