---
title: "RAVE Data Tools"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
build_pipeline <- raveio::configure_knitr()

# For debug use, try to mimic the environment of pipeline
# Load R scripts starting with `shared-` in R/ folder
.project_path <- rstudioapi::getActiveProject()
.module_id <- "compatibility_rave1"
lapply(
  list.files(
    file.path(.project_path, "modules", .module_id, "R"),
    pattern = "^shared-.*\\.R$",
    ignore.case = TRUE,
    full.names = TRUE
  ), 
  function(f){
    source(f, local = FALSE, chdir = TRUE)
    invisible()
  })

# Load variables in `settings.yaml` and expose them to the current environment
.settings <- raveio::load_yaml(file.path(
  .project_path, "modules", 
  .module_id, "settings.yaml"))
list2env(as.list(.settings), envir = environment())
```


```{rave load_subject_instance, language = "R", export = "subject"}
# Use strict=FALSE in case the subject is invalid
subject <- raveio::RAVESubject$new(
  project_name = project_name,
  subject_code = subject_code,
  strict = FALSE)
```


```{rave validate_subject, language = "R", export = "validate", cue = "always"}
validate <- raveio::validate_subject(
  subject = subject, 
  method = validation$mode, 
  version = validation$version)
```


## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-compatibility_rave1.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-compatibility_rave1.R")
```


Once the pipeline script `make-compatibility_rave1.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
Sys.setenv("RAVE_PIPELINE" = normalizePath("."))
try({
  raveio::pipeline_visualize()
}, silent = TRUE)
```







