---
title: "RAVE Pipeline - Reference"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
build_pipeline <- raveio::configure_knitr()

# Used to develop modules
if(FALSE){
  list2env(as.list(raveio::load_yaml(file.path(rstudioapi::getActiveProject(), "modules", "reference_module", "settings.yaml"))), envir = environment())
}
```



```{rave load_subject, language = "R", export = "subject", cue = "always", format = "rave-subject"}
subject <- raveio::RAVESubject$new(
  project_name = project_name, 
  subject_code = subject_code
)
```

Loads preset reference table, and generate a reference file called `_unsaved`. The reference table will be saved to this file before exported.

```{rave load_presets, language = "R", export = "reference_table_initial", cue = "always"}
if(isTRUE(reference_name %in% subject$reference_names)) {
  tryCatch({
    reference_table_initial <- subject$get_reference(reference_name, simplify = FALSE)
    
    reference_table_initial <- reference_table_initial[,c(
      "Electrode", "Group", "Reference", "Type"
    )]
    
  }, error = function(e){
    
    # log
    ravedash::logger("Unable to load reference [", reference_name, "]", level = "error")
    ravedash::logger_error_condition(e)
    stop("Unable to load reference [", reference_name, "]. Please check your reference file or simply start with a blank reference profile.")
  })
  
} else {
  # get electrode file
  electrode_table <- subject$get_electrode_table(reference_name = reference_name)
  
  # group by Label prefix
  str_electrode_group <- gsub("[0-9]+$", "", electrode_table$Label)
  electrode_table$Group <- trimws(str_electrode_group)
  
  if(!"LocationType" %in% names(electrode_table)) {
    electrode_table$LocationType <- "iEEG"
  } else {
    electrode_table$LocationType[!electrode_table$LocationType %in% raveio::LOCATION_TYPES] <- "iEEG"
  }
  if(length(subject$electrode_types) == nrow(electrode_table)) {
    electrode_table$SignalType <- subject$electrode_types
  } else if(!"SignalType" %in% names(electrode_table)) {
    electrode_table$SignalType <- "LFP"
  } else {
    electrode_table$SignalType[!electrode_table$SignalType %in% raveio::SIGNAL_TYPES] <- "LFP"
  }
  
  splits <- split(electrode_table, electrode_table$Group)
  
  
  subs <- lapply(splits, function(sub) {
    ltype <- sub$LocationType
    refs <- rep("noref", nrow(sub))
    ref_type <- rep("No Reference", nrow(sub))
    seeg <- which(ltype == 'sEEG')
    if(length(seeg) >= 2) {
      last_idx <- seeg[[length(seeg)]]
      refs[seeg[-length(seeg)]] <- sprintf("ref_%d", sub$Electrode[seeg[-1]])
      ref_type[seeg[-length(seeg)]] <- "Bipolar Reference"
      refs[[last_idx]] <- "noref"
      sub$Group[[last_idx]] <- "Bipolar-last-electrode"
    }
    sub$Reference <- refs
    sub$Type <- ref_type
    sub[, c("Electrode", "Group", "Reference", "Type")]
  })
  reference_table_initial <- do.call("rbind", unname(subs))
  
  # reference_table_initial <- data.frame(
  #   Electrode = subject$electrodes,
  #   Group = "Default",
  #   Reference = "noref",
  #   Type = "No Reference"
  # )
}
# save to subject's meta folder with reference name "_unsaved"
unsaved_meta <- file.path(subject$meta_path, "reference__unsaved.csv")
utils::write.csv(reference_table_initial, unsaved_meta)

```

```{rave load_voltage_data, language = "R", export = "voltage_data", cue = "always"}

electrodes <- subject$electrodes
blocks <- subject$blocks

cache_root <- file.path(subject$cache_path, "rave2", "voltage")
raveio::dir_create2(cache_root)

notch_params <- subject$preprocess_settings$notch_params

first_e <- electrodes[[1]]
first_inst <- raveio::new_electrode(subject = subject, 
                                number = first_e)

progress <- dipsaus::progress2("Check cache data", max = length(blocks), shiny_auto_close = TRUE)

voltage_signals <- lapply(blocks, function(block) {
  
  progress$inc(sprintf("%s", block))
  
  sample_signal <- raveio::load_h5(first_inst$voltage_file, name = sprintf("/raw/voltage/%s", block), ram = FALSE)
  signal_length <- length(sample_signal)
  
  block_path <- file.path(cache_root, block)
  exists <- TRUE
  
  arr <- tryCatch({
    filearray::filearray_checkload(
      filebase = block_path,
      mode = "readwrite", 
      symlink_ok = FALSE, 
      subject_id = subject$subject_id,
      blocks = blocks,
      electrodes = electrodes,
      notch_params = notch_params,
      sample_rates = subject$raw_sample_rates,
      signal_length = as.integer(signal_length),
      staged = TRUE
    )
  }, error = function(e){
    unlink(block_path, recursive = TRUE)
    arr <- filearray::filearray_create(
      filebase = block_path, 
      dimension = c(signal_length, length(electrodes)), 
      type = "double", partition_size = 1L
    )
    arr$.header$subject_id <- subject$subject_id
    arr$.header$blocks <- blocks
    arr$.header$electrodes <- electrodes
    arr$.header$notch_params <- notch_params
    arr$.header$sample_rates <- subject$raw_sample_rates
    arr$.header$signal_length <- as.integer(signal_length)
    arr$.save_header()
    exists <<- FALSE
    arr
  })
  
  list(
    exists = exists,
    array = arr
  )
  
})

names(voltage_signals) <- blocks

exists <- vapply(voltage_signals, '[[', FALSE, "exists")
missing_blocks <- blocks[!exists]

subject_id <- subject$subject_id

if(length(missing_blocks)) {
  
  dipsaus::lapply_async2(seq_along(electrodes), function(ii){
    e <- electrodes[[ii]]
    inst <- raveio::new_electrode(subject = subject_id, number = e)
    voltage_file <- inst$voltage_file
    for(block in missing_blocks) {
      s <- raveio::load_h5(voltage_file, sprintf("/raw/voltage/%s", block), ram = TRUE)
      voltage_signals[[block]]$array[, ii] <- s
    }
  }, plan = FALSE, callback = function(ii){
    sprintf("Creating cache|Electrode %s", electrodes[[ii]])
  })
  
}

voltage_data <- list(
  data = structure(lapply(voltage_signals, function(item){
    if(!item$exists) {
      item$array$set_header("staged", TRUE)
    }
    item$array$.mode <- "readonly"
    item$array
  }), names = blocks),
  electrodes = electrodes
)

```


```{rave validate_electrode_groups, language = "R", export = "reference_group"}

ngroups <- length(electrode_group)

group_names <- NULL
electrodes <- NULL

reference_group <- reference_table_initial
reference_group$GroupID <- 0

id <- 1
for(x in electrode_group) {
  e <- dipsaus::parse_svec(x$electrodes)
  if(length(e)){
    e <- unique(e)
    if(length(x$name) != 1 || !is.character(x$name)) {
      stop("Each electrode group must have a unique name")
    }
    
    x$name <- trimws(x$name)
    
    if(x$name %in% group_names) {
      stop("Electrode groups must have unique names (violation: ", x$name, ")")
    }
    group_names <- c(group_names, x$name)
    
    emissing <- e[!e %in% subject$electrodes]
    if(length(emissing)) {
      stop("Electrodes ", dipsaus::deparse_svec(emissing), " are not declared/imported. Please remove from group [", x$name, "]")
    }
    
    edup <- e[e %in% electrodes]
    if(length(edup)) {
      stop("Electrodes ", dipsaus::deparse_svec(edup), " have been included in multiple groups. Please fix this issue by ensuring each of these electrodes only belongs to one group at a time.")
    }
    electrodes <- c(electrodes, e)
    
    sel <- reference_group$Electrode %in% e
    reference_group$Group[sel] <- x$name
    reference_group$GroupID[sel] <- id
    
  }
  id <- id + 1
}

head(reference_group)


```

```{rave validate_and_apply_changes, language = "R", export = "reference_updated", cue = "always"}
reference_choices <- c(
  "No Reference", "Common Average Reference",
  "White-matter Reference", "Bipolar Reference"
)

for(item in changes) {
  
  evec <- dipsaus::parse_svec(item$electrodes)
  sel <- reference_group$Electrode %in% evec
    
  
  if(!any(sel)) { next }
  if(length(item$reference_type) != 1) {
    stop("Reference type is missing for electrode ", dipsaus::deparse_svec(evec))
  }
  
  reference_group$Type[sel] <- item$reference_type
  if(item$reference_type == reference_choices[[1]]) {
    reference_group$Reference[sel] <- "noref"
  } else if(
    item$reference_type %in% reference_choices[c(2,3)]
  ) {
    if(length(item$reference_signal) != 1) {
      stop("Reference signal must be the same within the group if the group reference type is common average or white-matter reference")
    }
    reference_group$Reference[sel] <- item$reference_signal
  } else if(item$reference_type == reference_choices[[4]]) {
    
    if(length(item$reference_signal) != sum(sel)) {
      stop("For Bipolar reference, `reference_signal` must have the same size as the number of electrodes")
    }
    reference_group$Reference[sel] <- item$reference_signal
  }
  
}

reference_updated <- reference_group
unsaved_meta <- file.path(subject$meta_path, "reference__unsaved.csv")
utils::write.csv(reference_updated, unsaved_meta)

```

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-reference_module.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-reference_module.R")
```


Once the pipeline script `make-reference_module.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
Sys.setenv("RAVE_PIPELINE" = normalizePath("."))
raveio::pipeline_visualize()
```

