---
title: "RAVE Fingerpting Markdown"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
ravepipeline::pipeline_setup_rmd("fingerprint_module")
rpymat::ensure_rpymat()
```

<!-- Begin: pipeline code -->


<!-- End: pipeline code -->

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-fingerprint_module.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-fingerprint_module.R")
```

#### Step 1: Create `RAVE` subject's instances

Noting that all the items in the `settings.yaml` are available as variables.

```{rave load_subject, language = "R", export = "subject", cue = "always", format = "rave-subject"}
# Load subject instance
subject <- raveio::RAVESubject$new(project_name = project_name, subject_code = subject_code)
```

#### Step 2: Initialize and load voltage data

```{rave load_voltage, language = "R", cue = "always", export = "repository", format = "rave_prepare_subject_voltage_with_epoch"}
repository <- raveio::prepare_subject_voltage_with_epoch(
  subject = subject,
  epoch_name = epoch_file_name,
  electrodes = load_electrodes,
  time_windows = time_window,
  reference = reference_name
)
```

```{python calculate_correlation, use_rave = TRUE, deps = c("input_data"), export = "correlation", cue = "thorough"}
# Load numpy
import numpy as np

# Calculate correlation
correlation = np.corrcoef(input_data['x'], input_data['y'])
print(correlation)
```


Once the pipeline script `make-fingerprint_module.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("ravepipeline")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```



