---
title: "RAVE Pipeline Markdown Template"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
build_pipeline <- raveio::configure_knitr()

# For debug use, try to mimic the environment of pipeline
# Load R scripts starting with `shared-` in R/ folder
.project_path <- rstudioapi::getActiveProject()
.module_id <- "custom_3d_viewer"
lapply(
  list.files(
    file.path(.project_path, "modules", .module_id, "R"),
    pattern = "^shared-.*\\.R$",
    ignore.case = TRUE,
    full.names = TRUE
  ), 
  function(f){
    source(f, local = FALSE, chdir = TRUE)
    invisible()
  })

# Load variables in `settings.yaml` and expose them to the current environment
.settings <- raveio::load_yaml(file.path(
  .project_path, "modules", 
  .module_id, "settings.yaml"))
list2env(as.list(.settings), envir = environment())
```

## Load subject and construct the brain instance

Obtain the project that contains subject and has valid brain files

```{rave get_valid_project_name, language = "R", export = "loaded_brain", cue = "always"}
rave_path <- raveio::raveio_getopt("data_dir")
raw_path <- raveio::raveio_getopt("raw_data_dir")

brain <- NULL
electrode_table <- NULL

if( !project_name %in% c("[Auto]", "[Upload]", "[None]") ) {
  # user specified
  if(isTRUE(has_fsdir(project_name = project_name, subject_code = subject_code, 
            rave_path = rave_path, raw_path = raw_path))) {
    subject <- raveio::RAVESubject$new(project_name = project_name, 
                                       subject_code = subject_code)
    # brain <- threeBrain::freesurfer_brain2(
    #   fs_subject_folder = subject$freesurfer_path,
    #   subject_name = subject_code, surface_types = c("pial", surface_types)
    # )
    brain <- raveio::rave_brain(subject, surfaces = c("pial", surface_types))
    brain$electrodes$objects <- list()
  }
  # get electrode table
  electrode_table <- raveio::load_meta2(meta_type = "electrodes", 
                                        project_name = project_name, 
                                        subject_code = subject_code)
}

if(!is.data.frame(electrode_table) && !project_name %in% c("[None]")) {
  electrode_table <- raveio::pipeline_load_extdata("suggested_electrode_table")
}

if(is.null(brain)) {
  # auto-search brain
  projects <- get_projects_with_scode(subject_code = subject_code, refresh = TRUE, 
                                      rave_path = rave_path)
  
  for(project in projects) {
    if( has_fsdir(project_name = project, subject_code = subject_code, 
            rave_path = rave_path, raw_path = raw_path) ) {
      subject <- raveio::RAVESubject$new(project_name = project, 
                                         subject_code = subject_code)
      brain <- raveio::rave_brain(subject, surfaces = c("pial", surface_types))
      brain$electrodes$objects <- list()
      project_name <- project
      break
    }
  }
}

if(is.null(brain)) {
  if( template_ok ) {
    brain <- threeBrain::merge_brain(template_surface_types = c(
      "pial", surface_types
    ))
    brain <- brain$template_object
  } else {
    stop("Cannot find a valid 3D model for this subject. Please construct the 3D models, or use a MNI template brain.")
  }
}

if(!is.null(brain) && is.data.frame(electrode_table)) {
  electrode_table$Subject <- brain$subject_code
  brain$set_electrodes(electrode_table)
}



loaded_brain <- list(
  subject_code = subject_code,
  project_name = project_name,
  brain = brain,
  electrode_table = electrode_table,
  surface_types = brain$surface_types
)
```

```{rave render_initial_viewer, language = "R", export = "initial_brain_widget"}
library(dipsaus)
force(shiny_outputId)
controllers <- as.list(controllers)
main_camera <- as.list(main_camera)

background <- controllers[["Background Color"]]
if(length(background) != 1) {
  background <- "#FFFFFF"
}

zoom_level <- main_camera$zoom
if(length(zoom_level) != 1 || zoom_level <= 0) {
  zoom_level <- 1
}

position <- as.numeric(unname(unlist(main_camera$position)))
up <- as.numeric(unname(unlist(main_camera$up)))
if(length(position) != 3 || length(up) != 3 ||
   all(position == 0) || all(up == 0) ||
   any(is.na(position)) || any(is.na(up))) {
  position <- c(0, 0, 500)
  up <- c(0, 1, 0)
} else {
  position <- position / sqrt(sum(position^2)) * 500
  up <- up / sqrt(sum(up^2))
}

if(!isTRUE(controllers[["Show Panels"]])) {
  controllers[["Show Panels"]] <- FALSE
}
    
initial_brain_widget <- loaded_brain$brain$plot(
  show_modal = FALSE,
  background = background,
  controllers = controllers,
  start_zoom = zoom_level,
  # send signals to update parameters such as camera, zoom-level...
  custom_javascript = raveio::glue(
    '
    // Remove the focus box
    if( canvas.focus_box ) {
      canvas.focus_box.visible = false;
    }
    
    // set camera
    canvas.main_camera.position.set(
      {{ position[[1]] }} , 
      {{ position[[2]] }} , 
      {{ position[[3]] }}
    );
    canvas.main_camera.up.set(
      {{ up[[1]] }} , 
      {{ up[[2]] }} , 
      {{ up[[3]] }}
    )
    canvas.main_camera.updateProjectionMatrix();

    // Let shiny know the viewer is ready
    if( canvas.shiny_mode ) {
      Shiny.setInputValue("{{ shiny_outputId }}", "{{Sys.time()}}");
    }

    // Force render one frame (update the canvas)
    canvas.start_animation(0);
    ',
    .open = "{{", .close = "}}"
  )
)

```

```{rave find_data_path, language = "R", export = "path_datatable", cue = "always"}
if(!length(data_source)) { data_source <- "None" }
path_datatable <- switch(
  data_source,
  "Uploads" = {
    get_subject_imaging_datapath(uploaded_source, subject_code = loaded_brain$subject_code, type = "uploads")
  }, 
  "Saved pipelines/modules" = {
    project_name <- data_source_project
    saved_pipeline <- data_source_pipeline
    saved_target <- data_source_pipeline_target
    
    if(!length(project_name)) {
      stop("Trying to get saved pipeline, but no project name has been given. Please assign a valid [data_source_project] variable. If you are running in RAVE's web interface, make sure the project name is set correctly")
    }
    if(!length(saved_pipeline) || !length(saved_target)) {
      stop("Trying to get saved pipeline, but no pipeline name nor target has been given. Please assign a valid [data_source_pipeline] & [data_source_pipeline_target] variable. If you are running in RAVE's web interface, make sure the pipeline is set with no errors.")
    }
    
    pipepath <- get_subject_imaging_datapath(
      saved_pipeline, subject_code = loaded_brain$subject_code,
      project_name = project_name, type = "pipeline"
    )
    if(!length(pipepath) || is.na(pipepath) || !dir.exists(pipepath)) {
      stop("Cannot find saved pipeline under the subject [",
           project_name, "/", loaded_brain$subject_code, "]: ",
           saved_pipeline)
    }
    
    structure(
      pipepath, 
      target = saved_target
    )
    
    # local({
    #   raveio:::activate_pipeline(pipepath)
    #   targets::tar_path(name = saved_target)
    # })
    
  },
  {
    NULL
  }
)
```

```{rave load_data_table, language = "R", export = "brain_with_data", cue = "always"}
loaded_datatable <- NULL

if(length(path_datatable) == 1) {
  if(!length(data_source)) { data_source <- "None" }
  switch(
    data_source,
    "Uploads" = {
      if(grepl("\\.fst$", path_datatable, ignore.case = TRUE)) {
        loaded_datatable <- raveio::load_fst(path_datatable, as.data.table = TRUE)
      }
    },
    "Saved pipelines/modules" = {
      
      var <- raveio::pipeline_read(
        var_names = attr(path_datatable, "target"),
        pipe_dir = path_datatable,
        ifnotfound = NULL
      )
      
      if(length(var)) {
        try({
          
          if("Electrode" %in% names(var)) {
            
            if(!is.data.frame(var)) {
              var <- as.data.frame(var)
            }
            loaded_datatable <- var
          }
          
        })
      }
      
    }
  )
}


nms <- names(loaded_datatable)

if(!"Electrode" %in% nms && length(path_datatable)) {
  if(isTRUE(data_source %in% c("Uploads", "Saved pipelines/modules"))) {
    stop("Cannot set electrode values. Please make sure the data is a named table, and one of the table names must be [Electrode] (case-sensitive).")
  }
} 
  

if(is.data.frame(loaded_datatable) && "Electrode" %in% nms) {
  
  if(!data.table::is.data.table(loaded_datatable)) {
    loaded_datatable <- data.table::as.data.table(loaded_datatable)
  }
  
  # subset if Subject is contained
  if("Subject" %in% nms) {
    template_subject <- raveio::raveio_getopt("threeBrain_template_subject", default = "N27")
    
    if(!identical(loaded_brain$brain$subject_code, 
                  template_subject)) {
      loaded_datatable <- loaded_datatable[loaded_datatable$Subject %in% loaded_brain$brain$subject_code, ]
    }
  }
  
  if("Time" %in% names(loaded_datatable)) {
    
    # Need to make sure each time-component has only one value
    fct <- sprintf(
      "%.2f__%.0f", 
      loaded_datatable$Time,
      loaded_datatable$Electrode)
    
    # Remove names that don't name sense to collapse
    # Can't care less about others
    nms <- nms[!nms %in% c("Time", "Electrode", "Trial", "Frequency", "Block", "Subject")]
    
    coltypes <- sapply(nms, function(nm) {
      is.numeric(loaded_datatable[[nm]])
    }, simplify = FALSE, USE.NAMES = TRUE)
    
    
    new_table <- lapply(split(loaded_datatable, fct), function(sub) {
      if(nrow(sub) == 1) {
        return(sub[, c(nms, "Electrode", "Time"), drop = FALSE])
      }
      re <- sapply(nms, function(nm){
        v <- sub[[nm]]
        if(coltypes[[nm]]) {
          v <- v[!is.na(v)]
          if(!length(v)) { return(NA_real_) }
          return(mean(v))
        } else {
          v <- table(v)
          v <- v[!is.na(v)]
          if(!length(v)) { return(NA) }
          v <- names(v)[v == max(v)]
          if(length(v) > 1) { return(NA) }
          return(v)
        }
      }, simplify = FALSE, USE.NAMES = TRUE)
      re$Electrode <- sub$Electrode[[1]]
      re$Time <- sub$Time[[1]]
      as.data.frame(re)
    })
    
    loaded_datatable <- data.table::rbindlist(new_table, use.names = TRUE)
  }
  nms <- names(loaded_datatable)
  invalids <- vapply(nms, function(nm) {
    all(is.na(loaded_datatable[[nm]]))
  }, FALSE)
  nms <- nms[!invalids]
  # loaded_datatable <- loaded_datatable[, !invalids, with = FALSE]
  
  if(nrow(loaded_datatable)) {
    loaded_brain$brain$set_electrode_values(loaded_datatable)
  } else {
    nms <- NULL
  }
}
  
brain_with_data <- list(
  brain = loaded_brain$brain,
  variables = nms
)
```


```{rave render_viewer, language = "R", export = "brain_widget", cue = "always"}
library(dipsaus)
force(shiny_outputId)
controllers <- as.list(controllers)
main_camera <- as.list(main_camera)

background <- controllers[["Background Color"]]
if(length(background) != 1) {
  background <- "#FFFFFF"
}

zoom_level <- main_camera$zoom
if(length(zoom_level) != 1 || zoom_level <= 0) {
  zoom_level <- 1
}

position <- as.numeric(unname(unlist(main_camera$position)))
up <- as.numeric(unname(unlist(main_camera$up)))
if(length(position) != 3 || length(up) != 3 ||
   all(position == 0) || all(up == 0) ||
   any(is.na(position)) || any(is.na(up))) {
  position <- c(0, 0, 500)
  up <- c(0, 1, 0)
} else {
  position <- position / sqrt(sum(position^2)) * 500
  up <- up / sqrt(sum(up^2))
}

# find valid names
dnames <- brain_with_data$variables
dnames <- dnames[!dnames %in% c("Project", "Subject", "Electrode", "Time", "Label")]

dname <- controllers[["Display Data"]] %OF% dnames

if(!identical(controllers[["Display Data"]], dname) && length(dname)) {
  controllers[["Display Data"]] <- dname
  controllers[["Display Range"]] <- ""
}

if(!isTRUE(controllers[["Show Panels"]])) {
  controllers[["Show Panels"]] <- FALSE
}
    
brain_widget <- brain_with_data$brain$plot(
  show_modal = FALSE,
  background = background,
  controllers = controllers,
  start_zoom = zoom_level,
  # send signals to update parameters such as camera, zoom-level...
  custom_javascript = raveio::glue(
    '
    // Remove the focus box
    if( canvas.focus_box ) {
      canvas.focus_box.visible = false;
    }
    
    // set camera
    canvas.main_camera.position.set(
      {{ position[[1]] }} , 
      {{ position[[2]] }} , 
      {{ position[[3]] }}
    );
    canvas.main_camera.up.set(
      {{ up[[1]] }} , 
      {{ up[[2]] }} , 
      {{ up[[3]] }}
    )
    canvas.main_camera.updateProjectionMatrix();

    // Let shiny know the viewer is ready
    if( canvas.shiny_mode ) {
      Shiny.setInputValue("{{ shiny_outputId }}", "{{Sys.time()}}");
    }

    // Force render one frame (update the canvas)
    canvas.start_animation(0);
    ',
    .open = "{{", .close = "}}"
  )
)

```

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-custom_3d_viewer.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-custom_3d_viewer.R")
```


Once the pipeline script `make-custom_3d_viewer.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
Sys.setenv("RAVE_PIPELINE" = normalizePath("."))
try({
  raveio::pipeline_visualize()
}, silent = TRUE)
```







