---
title: "RAVE Pipeline Markdown Template"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
raveio::pipeline_setup_rmd("multitaper_explorer")
```

```{rave load_subject, language = "R", export = "subject", cue = "always", format = "rave-subject"}
# Load subject instance
subject <- raveio::RAVESubject$new(project_name = project_name, subject_code = subject_code)
```

With `export="subject"`, the subject variable will be registered for the following chunks to use. Be aware that all other variables created in this block will not be exposed.

#### Step 2: Initialize and load voltage data

```{rave load_voltage, language = "R", cue = "always", export = "repository", format = "rave_prepare_subject_voltage_with_epoch"}
repository <- raveio::prepare_subject_voltage_with_epoch(
  subject = subject,
  epoch_name = epoch_file_name,
  electrodes = load_electrodes,
  time_windows = time_window,
  reference = reference_name
  
)
```

### Step 3: Run multitaper and get result for all conditions
```{rave find_multitaper, language = "R", export = "multitaper_result"}
multitaper_result <- generate_multitaper(repository, load_electrodes, frequency_range, 
                                         time_bandwidth, num_tapers, window_params, min_nfft, 
                                         weighting, detrend_opt, parallel)
```
  
### Step 4: get heatmap data from multitaper result for each spectral range for a specific condition
```{rave find_heatmap, language = "R", export = "heatmap_result"}
heatmap_result <- generate_heatmap(repository, multitaper_result, time_window,
                             analysis_windows, load_electrodes,
                             window_params, condition, label) 
```
  
  #### Step 5: Visualize Heatmaps for all the generated spectral ranges for a specific condition
```{r}
for(i in 1:length(heatmap_result)) {
  p <- plot_heatmap(heatmap_result[[i]], SOZ_elec = SOZ_elec, plot_SOZ_elec = plot_SOZ_elec, resect_elec, plot_resect_elec, name_type = label, organize_top = organize_top, repository = repository, subject_code = subject_code, analysis_windows, index = i, text_size)
  print(p)
}
```

  #### Step 6: Save file for 3D brain display for each spectral result
```{rave electrode_powertime, language = "R", export = "YAEL_data"}
YAEL_data <- electrode_powertime(
  heatmap_result, 
  subject_code = subject_code ,
  analysis_windows = analysis_windows,
  SOZ_elec = SOZ_elec,
  resect_elec = resect_elec,
  load_electrodes = load_electrodes
) 
```

  #### Step 6: Analyze data and find start and duration for bands greater than 2 z-scores
```{rave analyze_zscore, language = "R", export = "analysis_data"}
for(i in 1:length(heatmap_result)) {
  analysis_data <- analyze_zscore(
    heatmap_result[[i]], 
    repository,
    window_params,
    time_stat_start,
    time_stat_end
  ) 
  # Print results
  cat("Frequency: ", analysis_windows[[i]]$frequency_range[1], " - ", analysis_windows[[i]]$frequency_range[2], "\n")
  for (j in 1:length(analysis_data$Start)) {
    if (!is.na(analysis_data$Start[j])) {
      cat("Electrode:", analysis_data$Electrodes[j], 
          "Start:", analysis_data$Start[j], 
          "Length:", analysis_data$Length[j], "\n")
    }
  }
}

```

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-multitaper_explorer.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-multitaper_explorer.R")
```


Once the pipeline script `make-multitaper_explorer.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
# Fixed usage, show pipeline graph
try({
  asNamespace("raveio")$pipeline_dependency_graph(
    pipeline_path = ".", glimpse = TRUE)
}, silent = TRUE)
```




