---
title: "Explore Stimulation Data"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
build_pipeline <- raveio::configure_knitr()

# For debug use, try to mimic the environment of pipeline
# Load R scripts starting with `shared-` in R/ folder
.project_path <- rstudioapi::getActiveProject()
.module_id <- "stimulation_explorer"
lapply(
  list.files(
    file.path(.project_path, "modules", .module_id, "R"),
    pattern = "^shared-.*\\.R$",
    ignore.case = TRUE,
    full.names = TRUE
  ), 
  function(f){
    source(f, local = FALSE, chdir = TRUE)
    invisible()
  })

# Load variables in `settings.yaml` and expose them to the current environment
.settings <- raveio::load_yaml(file.path(
  .project_path, "modules", 
  .module_id, "settings.yaml"))
list2env(as.list(.settings), envir = environment())
```


```{rave load_subject, language = "R", export = "subject"}
library(raveio)
subject <- RAVESubject$new(
  project_name = project_name, 
  subject_code = subject_code
)
subject
```


```{rave load_repository, language = "R", export = "repository", cue="always"}
trial_interval <- sort(c(epoch_choice__trial_starts, epoch_choice__trial_ends))
repository <- raveio::prepare_subject_voltage_with_epoch(
  subject = subject,
  electrodes = loaded_electrodes,
  epoch = epoch_choice,
  reference_name = reference_name,
  time_windows = trial_interval,
  quiet = TRUE
)
repository
```

```{rave get_analysis_electrodes, language = "R", export = "analysis_electrodes2", cue="always"} 
analysis_electrodes2 <- dipsaus::parse_svec(analysis_electrodes)
analysis_electrodes2 <- analysis_electrodes2[analysis_electrodes2 %in% repository$electrode_list]
if(!length(analysis_electrodes2)) {
  stop("No valid analysis electrodes set.")
}
dipsaus::deparse_svec(analysis_electrodes2)
```

Clean baseline settings, check if there is any errors and get necessary parameters

```{rave get_baseline_settings, language = "R", export = "baseline_settings2"}
if(is.list(baseline_settings)) {
  baseline_method <- baseline_settings$method
  baseline_source <- baseline_settings$source
  baseline_global <- isTRUE(baseline_settings$global)
  baseline_window <- unlist(baseline_settings$window)
  if(length(baseline_method) == 1 && 
     is.character(baseline_method)) {
    
    baseline_method <- match.arg(tolower(baseline_method), c(
      "percentage", "zscore", "subtract_mean"
    ))
    
    # check baseline source: block number or NULL/""
    if(length(baseline_source) &&
       nzchar(trimws(baseline_source))) {
      baseline_from_block <- TRUE
      baseline_source <- unique(unlist(baseline_source))
      missing_blocks <- baseline_source[!baseline_source %in% subject$blocks]
      if(length(missing_blocks)) {
        stop(sprintf("Baseline from session block: the block [%s] does not exist or have not been imported.", paste(missing_blocks, collapse = ",")))
      }
      
      # # Get baseline mean and sd
      # msd <- dipsaus::lapply_async2(repository$electrode_instances, function(inst) {
      #   s <- inst$load_blocks(blocks = baseline_source, type = data_type, simplify = FALSE)
      #   return(c(mean(s, na.rm = TRUE), stats::sd(s, na.rm = TRUE), length(s)))
      # }, plan = FALSE)
      # 
      # msd <- do.call("rbind", msd)
      # if(baseline_global) {
      #   msd[,1] <- mean(msd[,1])
      #   df_ratio <- (msd[,3] - 1) / (sum(msd[,3]) - 1)
      #   msd[,2] <- sqrt(sum(msd[,2]^2 * df_ratio))
      # }
      
      
      baseline_settings2 <- list(
        has_baseline = TRUE,
        method = baseline_method,
        global = baseline_global,
        source = baseline_source,
        # mean =  msd[,1],
        # sd = msd[,2],
        per_trial = FALSE
      )
      # raveio::voltage_baseline(
      #   x = repository, baseline_windows = NULL, method = baseline_method, 
      #   baseline_mean = msd[,1], baseline_sd = msd[,2])
      
    } else {
      if(baseline_global) {
        stop("Per-trial baseline does not support global baseline.")
      }
      baseline_window <- raveio::validate_time_window(baseline_window)
      baseline_settings2 <- list(
        has_baseline = TRUE,
        method = baseline_method,
        global = FALSE,
        window = baseline_window,
        per_trial = TRUE
      )
      # raveio::voltage_baseline(
      #     x = repository, baseline_windows = baseline_window, 
      #     method = baseline_method)
      
    }
    
  } 
  
  
} else {
  nelec <- length(repository$electrode_list)
  baseline_settings2 <- list(
    has_baseline = FALSE
  )
  # raveio::voltage_baseline(
  #         x = repository, baseline_windows = NULL, method = "zscore", 
  #         baseline_mean = rep(0, nelec), baseline_sd = rep(1, nelec))
}
```

```{rave get_baseline_data, language = "R", export = "baseline_data"}
if(!baseline_settings2$has_baseline) {
  raveio::voltage_baseline(
    x = repository,
    # baseline_windows = baseline_settings2$window,
    method = baseline_settings2$method,
    units = c("Trial", "Electrode"),
    baseline_mean = rep(0, length(repository$electrode_list)),
    baseline_sd = rep(1, length(repository$electrode_list))
  )
} else {
  if(!baseline_settings2$per_trial) {
    # load blocks of data, calculate pwelch
    .NotYetImplemented()
  } else {
    # per-trial baseline
    raveio::voltage_baseline(
      x = repository,
      baseline_windows = baseline_settings2$window,
      method = baseline_settings2$method,
      units = c("Trial", "Electrode"), 
      electrodes = analysis_electrodes2
    )
  }
}
baseline_data <- repository$voltage$baselined
baseline_data$.mode <- "readwrite"
baseline_data$set_header("sample_rate", repository$sample_rate)
baseline_data$.mode <- "readonly"
```

```{rave get_interpolate_settings, language = "R", export = "interpolate_settings"}
interpolate_settings <- FALSE
if(is.list(interpolate)) {
  # TODO: add B-spline
  method <- match.arg(interpolate$method, c("linear", "none", "B-spline")) 
  if(method != "none") {
    cname1 <- sprintf("Event_%s", interpolate$from)
    cname2 <- sprintf("Event_%s", interpolate$to)
    epoch_columns <- tolower(c("event_onset", names(repository$epoch_table)))
    if(
      isTRUE(tolower(cname1) %in% epoch_columns) &&
      isTRUE(tolower(cname2) %in% epoch_columns) &&
      !identical(tolower(cname1), tolower(cname2))
    ) {
      col1 <- which(epoch_columns == tolower(cname1)) - 1
      col2 <- which(epoch_columns == tolower(cname2)) - 1
      # measured in ms
      if(col1 == 0) {
        interp_starts <- repository$epoch_table$Time
      } else {
        interp_starts <- repository$epoch_table[[col1]]
      }
      if(col2 == 0) {
        interp_ends <- repository$epoch_table$Time
      } else {
        interp_ends <- repository$epoch_table[[col2]]
      }
      
      interpolate_settings <- list(
        method = method,
        starts = interp_starts - repository$epoch_table$Time,
        ends = interp_ends - repository$epoch_table$Time,
        sample_rate = repository$sample_rate
      )
    } else {
      warning(sprintf("No interpolation will be done: interpolation start [%s] and to [%s] must be length of one, non-identical, and must exist in epoch table.", paste(cname1, collapse = ","), paste(cname2, collapse = ",")))
    }
  }
}
```

```{rave interpolate_signals, language = "R", export = "interpolated_data"}
interpolated_data <- baseline_data
dnames <- dimnames(baseline_data)
electrodes <- as.integer(dnames$Electrode)
time <- as.double(dnames$Time)
fbase <- baseline_data$.filebase
time_windows <- unlist(repository$time_windows)

if(is.list(interpolate_settings)) {
  fbase2 <- file.path(fbase, "interpolated")
  
  interpolated_data <- filearray::filearray_load_or_create(
    filebase = fbase2, dimension = dim(baseline_data), type = "float", 
    partition_size = 1L, initialize = FALSE, symlink_ok = FALSE,
    verbose = FALSE, mode = "readwrite", interpolate_settings = interpolate_settings,
    on_missing = function(arr) {
      dimnames(arr) <- dnames
    }
  )
  interpolated_electrodes <- interpolated_data$get_header("interpolated_electrodes", NULL)
  
  todos <- analysis_electrodes2[!analysis_electrodes2 %in% interpolated_electrodes & analysis_electrodes2 %in% electrodes]
  
  stim_onset <- floor(
    (interpolate_settings$starts - time_windows[[1]]) *
      interpolate_settings$sample_rate
  ) + 1
  stim_offset <- ceiling(
    (interpolate_settings$ends - time_windows[[1]]) *
      interpolate_settings$sample_rate
  ) + 1
  
  if(length(todos)) {
    switch(
      interpolate_settings$method,
      "linear" = {
        dipsaus::lapply_async2(todos, function(e) {
          sel <- which(electrodes %in% e)[[1]]
          slice <- baseline_data[, , sel, drop = TRUE, dimnames = FALSE]
          tmp <- sapply(seq_along(stim_offset), function(ii) {
            s <- slice[, ii]
            onset_idx <- stim_onset[[ii]]
            offset_idx <- stim_offset[[ii]]
            if(onset_idx < 1) { onset_idx <- 1 }
            if(onset_idx > length(s)) { onset_idx <- length(s) }
            if(offset_idx > length(s)) { offset_idx <- length(s) }
            if(offset_idx - onset_idx > 1) {
              a <- s[onset_idx]
              b <- s[offset_idx]
              idx <- seq.int(0, offset_idx - onset_idx)
              s[idx + onset_idx] <- (b - a) / (offset_idx - onset_idx) * idx + a
            }
            s
          })
          interpolated_data[, , sel] <- tmp
          return()
        }, plan = FALSE)
      },
      {
        stop("Interpolate method hasn't been implemented yet: ", interpolate_settings$method)
      }
    )
    
    interpolated_electrodes <- sort(c(interpolated_electrodes, todos))
    interpolated_data$set_header("interpolated_electrodes", interpolated_electrodes)
  }
  interpolated_data$.mode <- "readonly"
}
```
TODO: time-lock event

```{rave shift_and_downsample_data, language = "R", export = "shifted_downsampled_data"}
shifted_downsampled_data <- interpolated_data

analysis_event2 <- NULL
if(length(analysis_event) == 1 && tolower(analysis_event) != "onset") {
  # check if the analysis_event is in epoch column
  sel <- names(repository$epoch_table) == sprintf("Event_%s", analysis_event)
  if(any(sel)) {
    analysis_event2 <- names(repository$epoch_table)[sel][[1]]
  }
}

downsample <- as.integer(downsample)
if(isTRUE(downsample > 1) || length(analysis_event2)) {
  
  # create a sub-array within interpolated_data file base
  fbase <- file.path(interpolated_data$.filebase, "shifted_downsampled")
  dnames <- dimnames(interpolated_data)
  electrodes <- as.integer(dnames$Electrode)
  time <- as.double(dnames$Time)
  dim0 <- dim(interpolated_data)
  
  decimated_time <- as.double(time[seq(1, length(time), by = downsample)])
  dnames$Time <- decimated_time
  dim <- dim0
  dim[[1]] <- length(decimated_time)
  shifted_downsampled_data <- filearray::filearray_load_or_create(
    filebase = fbase, dimension = dim, type = "float", 
    symlink_ok = FALSE, mode = "readwrite", initialize = FALSE, partition_size = 1L, 
    verbose = FALSE, analysis_event = analysis_event2, downsample = downsample,
    epoch_table = repository$epoch_table,
    on_missing = function(arr) {
      dimnames(arr) <- dnames
      arr$set_header("sample_rate", repository$sample_rate / downsample)
    }
  )
  
  # shift data
  if(length(analysis_event2)) {
    event_time <- repository$epoch_table[[analysis_event2]]
    shift_amount <- round((event_time - repository$epoch_table$Time) * repository$sample_rate / downsample)
  } else {
    shift_amount <- NULL
  }
  
  shifted_electrodes <- shifted_downsampled_data$get_header("shifted_electrodes", NULL)
  todos <- analysis_electrodes2[!analysis_electrodes2 %in% shifted_electrodes & analysis_electrodes2 %in% electrodes]
  
  if(length(todos)) {
    dipsaus::lapply_async2(todos, function(e) {
      idx <- which(electrodes == e)[[1]]
      slice <- interpolated_data[, , idx, drop = FALSE, dimnames = FALSE, reshape = dim0[c(1,2)]]
      if(downsample > 1) {
        slice <- apply(slice, 2, function(s) {
          ravetools::decimate(s, q = downsample, ftype = "fir")
        })
      }
      if(length(shift_amount)) {
        # shift array
        slice <- dipsaus::shift_array(slice, shift_idx = 1L, shift_by = 2L, shift_amount = shift_amount)
        slice[!is.finite(slice)] <- NA_real_
      }
      shifted_downsampled_data[,, idx] <- slice
      return()
    }, plan = FALSE, callback = function(e) {
      sprintf("Down-sample & event alignment|Electrode %d", e)
    })
    shifted_electrodes <- sort(c(shifted_electrodes, todos))
    shifted_downsampled_data$set_header("shifted_electrodes", shifted_electrodes)
  }
  
}
```

```{rave build_condition_groups, language = "R", export = "condition_groups2"}
condition_groups2 <- dipsaus::drop_nulls(
  lapply(seq_along(condition_groups), function(ii) {
    g <- condition_groups[[ii]]
    group_name <- g$group_name
    if(length(group_name) != 1 || !nzchar(trimws(group_name))) {
      group_name <- sprintf("Group %d", ii)
    }
    conditions <- sort(unique(unlist(g$group_conditions)))
    selection <- repository$epoch_table$Condition %in% conditions
    if(!length(conditions) || !any(selection)) {
      return(NULL)
    }
    
    list(
      order = ii,
      group_name = group_name,
      conditions = conditions,
      selection = selection
    )
  })
)
```

## Plots

```{rave plot_data_single_electrode_trial_by_time, language = "R", export = "plot_data_trial_by_time"}
dnames <- dimnames(shifted_downsampled_data)
sample_rate <- shifted_downsampled_data$get_header("sample_rate")

array_data <- shifted_downsampled_data[,, repository$electrode_list %in% analysis_electrodes2, dimnames = FALSE, drop = FALSE]
array_data <- ravetools::collapse(array_data, keep = c(1, 2))

data <- lapply(condition_groups2, function(g) {
  sub <- array_data[, g$selection, drop = FALSE]
  mse <- apply(sub, 1, dipsaus::mean_se, na.rm = TRUE,
               se_na_as_zero = FALSE)
  g$mean <- mse[1,]
  g$se <- mse[2,]
  
  rgs <- g$mean[is.finite(g$mean)]
  if(length(rgs)) {
    g$range <- range(rgs)
  } else {
    g$range <- c(-1e-6,1e-6)
  }
  g
})

# reshape data
group_order <- sapply(data, '[[', "order")
group_names <- sapply(data, '[[', "group_name")
group_mean <- sapply(data, '[[', "mean")

plot_data_trial_by_time <- list(
  time = as.double(dnames$Time),
  sample_rate = sample_rate,
  group_order = group_order,
  group_names = group_names,
  group_mean = group_mean,
  group_data = data
)
```

```{r plot_trial_by_time_per_cond}
plot_trial_by_time_per_condtion(
  plot_data_trial_by_time, style = "vstack"
)
```

```r

{rave plot_single_electrode_trial_by_time, language = "R", export = "plot_data_trial_by_time"}
array_data <- shifted_data[,, repository$electrode_list %in% analysis_electrodes2, dimnames = FALSE, drop = TRUE]
if(length(dim(array_data)) > 2) {
  array_data <- ravetools::collapse(array_data, keep = c(1, 2))
}

ravetools::plot_signals(t(array_data[,1:10]), repository$sample_rate / downsample, space = 0.95)

plot_data_trial_by_time <- list()
```


## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-stimulation_explorer.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-stimulation_explorer.R")
```


Once the pipeline script `make-stimulation_explorer.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
Sys.setenv("RAVE_PIPELINE" = normalizePath("."))
try({
  raveio::pipeline_visualize()
}, silent = TRUE)
```







