---
title: "RAVE System Snapshot"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
build_pipeline <- raveio::configure_knitr()

# For debug use, try to mimic the environment of pipeline
# Load R scripts starting with `shared-` in R/ folder
.project_path <- rstudioapi::getActiveProject()
.module_id <- "configure_rave"
lapply(
  list.files(
    file.path(.project_path, "modules", .module_id, "R"),
    pattern = "^shared-.*\\.R$",
    ignore.case = TRUE,
    full.names = TRUE
  ), 
  function(f){
    source(f, local = FALSE, chdir = TRUE)
    invisible()
  })

# Load variables in `settings.yaml` and expose them to the current environment
.settings <- raveio::load_yaml(file.path(
  .project_path, "modules", 
  .module_id, "settings.yaml"))
list2env(as.list(.settings), envir = environment())
```

## System summary

```{rave get_system_summary, language = "R", export = "system_summary", cue = "always"}
session_info <- utils::sessionInfo()

# Get math libraries
blas <- session_info$BLAS
if (is.null(blas)) { blas <- "" }
lapack <- session_info$LAPACK
if (is.null(lapack)) { lapack <- "" }

# Get current path
raw_dir <- raveio::raveio_getopt("raw_data_dir", default = "<Missing>")
data_dir <- raveio::raveio_getopt("data_dir", default = "<Missing>")
cache_dir <- raveio::cache_root()

    healthy_directory <- function(path){
      ifelse(dir.exists(path), "[healthy]", "[unable to reach]")
    }

    package_ver <- function(name, version_only = FALSE) {
      suppressWarnings({
        if(name %in% names(session_info$otherPkgs)) {
          desc <- session_info$otherPkgs[[name]]
        } else if(name %in% names(session_info$loadedOnly)) {
          desc <- session_info$loadedOnly[[name]]
        } else {
          desc <- utils::packageDescription(name, drop = TRUE)
        }
      })

      if(!inherits(desc, "packageDescription")) { return(NULL) }

      if(version_only) {
        return(desc$Version)
      }
      sprintf("%s [%s]", desc$Package, desc$Version)

    }


    # get basic information
    cat(
      sep = "",
      "Operating system:\n",
      "  OS type:         ", session_info$platform, "\n",
      "  OS name:         ", session_info$running, "\n",
      "  File separator:  ", .Platform$file.sep, "\n",
      "  Endianess:       ", .Platform$endian, "\n",

      "\nR information\n",
      "  Version:         ", session_info$R.version$version.string, "\n",
      "  Architecture:    ", session_info$R.version$arch, "\n",
      "  Matrix products: ", session_info$matprod, "\n",
      local({
        if (blas == lapack && nzchar(blas))
          c("  BLAS/LAPACK:     ", blas, "\n", sep = "")
        else {
          if (nzchar(blas)) {
            c("  BLAS:            ", blas, "\n", sep = "")
          }
          if (nzchar(lapack)) {
            c("  LAPACK:          ", lapack, "\n", sep = "")
          }
        }
      }),

      "\nRAVE status\n",
      "  Version:        ", package_ver("rave", version_only = TRUE), "\n",
      "  Template brain: ", raveio::raveio_getopt('threeBrain_template_subject', default = "N27"), "\n",
      "  Directories:    ",
      "Raw ", healthy_directory(raw_dir), ", ",
      "Main ", healthy_directory(data_dir), ", ",
      "Session ", healthy_directory(cache_dir), "\n",

      "  Core dependencies: \n",
      "    ", package_ver("dipsaus"), ", ",
      package_ver("filearray"), ", ",
      package_ver("future"), ", ",

      "\n    ",
      package_ver("ravedash"), ", ",
      package_ver("raveio"), ", ",
      package_ver("ravetools"), ", ",

      "\n    ", package_ver("shiny"), ", ",
      package_ver("targets"), ", ",
      package_ver("threeBrain"), ", ",



```

With `export="subject"`, the subject variable will be registered for the following chunks to use. Be aware that all other variables created in this block will not be exposed.

#### Step 2: Load epoch and reference information

```{rave load_epoch, language = "R", export = "epoch_instance"}
epoch_instance <- raveio::RAVEEpoch$new(subject, epoch)
head(epoch_instance$update_table())
```

```{rave load_reference, language = "R", export = "reference_table"}
reference_table <- subject$meta_data(
  meta_type = "reference", reference)
head(reference_table)
```

#### Step 3: Initialize and load power data

Initialize the electrode instances and register the epoch, reference information

```{rave load_electrodes, language = "R", export = "electrode_instances"}
requested_electrodes <- dipsaus::parse_svec(electrodes)
requested_electrodes <- requested_electrodes[
  requested_electrodes %in% subject$electrodes]
electrode_instances <- lapply(requested_electrodes, function(ei){
  e <- raveio::new_electrode(subject, number = ei, signal_type = "LFP")
  
  # set epoch
  e$set_epoch(epoch_instance)

  # set epoch range (-1 to 2 seconds relative to onset)
  e$trial_intervals <- intervals

  # set reference
  ref_name <- subset(reference_table, Electrode == ei)[["Reference"]]
  e$set_reference(ref_name)
  e
})
names(electrode_instances) <- requested_electrodes
```


Start to load power. Here also create cache to the `RAVE` cache directory.

```{rave load_and_cache_power, language = "R", export = "power"}
power_list <- lapply(electrode_instances, function(e){
  e$load_data("power")
})
target <- normalizePath(file.path("shared", "cache", "power"),
                        mustWork = FALSE)
  
if(dir.exists(target)){
  unlink(target, recursive = TRUE, force = TRUE)
} else {
  raveio::dir_create2(dirname(target))
}
power <- filearray::filearray_bind(
  .list = power_list, symlink = TRUE, 
  filebase = target)

if(length(power_list)){
  dnames <- dimnames(power_list[[1]])
  dnames[[4]] <- as.integer(names(electrode_instances))
  dimnames(power) <- dnames
} else {
  stop("No power data not loaded")
}
```

#### Step 4: Baseline correction

```{rave calculate_baseline, language = "R", export = "baseline_data"}
dim <- dim(power)
dim[length(dim)] <- 1
plen <- prod(dim)
target <- file.path(electrode_instances[[1]]$cache_root, "..")
raveio::dir_create2(target)
target <- normalizePath(target, mustWork = TRUE)
target <- file.path(target, "_baseline")
if(dir.exists(target)){
  output <- filearray::filearray_load(target, "readwrite")
  if(!all(dim(output) == dim(power))){
    output$delete()
  }
  if(!identical(dimnames(output), dimnames(power))){
    dimnames(output) <- dimnames(power)
  }
}
if(!dir.exists(target)){
  output <- filearray::filearray_create(
    filebase = target,
    dimension = dim(power),
    type = "float",
    partition_size = 1L
  )
}

bl_range <- unlist(baseline)
dnames <- dimnames(power)
baseline_indexpoints <- which(
  dnames$Time >= bl_range[[1]] & dnames$Time <= bl_range[[2]])

filearray::fmap(power, function(input){
  x <- input[[1]]
  dim(x) <- dim
  bl <- dipsaus::baseline_array(
    x, along_dim = 2L,
    baseline_indexpoints = baseline_indexpoints,
    method = baseline_method
  )
  bl
}, .y = output, .input_size = plen)

baseline_data <- output
```


#### Step 5: Collapse baseline data

```{rave collapse_by_trial_and_electrodes, language = "R", export = "collapsed"}

dim <- dim(baseline_data)
dim[length(dim)] <- 1
plen <- prod(dim)
collase_by_trial <- filearray::fmap2(baseline_data, function(input){
  x <- input[[1]]
  dim(x) <- dim
  dipsaus::collapse(x, keep = c(2,1), average = TRUE)
}, .input_size = plen, .simplify = TRUE)

collapsed <- list(
  collase_by_trial = collase_by_trial,
  collase_by_trial_electrodes = dipsaus::collapse(
    collase_by_trial, keep = c(1, 2), average = TRUE)
)
```

```{r}
brain <- threeBrain::freesurfer_brain2(
  fs_subject_folder = subject$freesurfer_path, subject_name = subject$subject_code
)
brain$plot()
```

#### Step 6: Visualize

```{rave plot_heatmap_collase_by_trial_electrodes, export = "collase_by_trial_timestamp", cue="always"}

# Timestamp of when the plot is created
collase_by_trial_timestamp <- Sys.time()

# visualize
dnames <- power$dimnames()

image(
  collapsed$collase_by_trial_electrodes,
  y = dnames$Frequency,
  ylab = "Frequency (Hz)",
  x = dnames$Time, 
  xlab = "Time (s)",
  main = "Mean power across trial and electrodes"
)

```

## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-configure_rave.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-configure_rave.R")
```


Once the pipeline script `make-configure_rave.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
Sys.setenv("RAVE_PIPELINE" = normalizePath("."))
try({
  raveio::pipeline_visualize()
}, silent = TRUE)
```


```{r execute}
Sys.setenv("RAVE_PIPELINE" = normalizePath("."))
raveio::pipeline_run(type = "vanilla")
raveio::pipeline_progress(method = 'details')
```






