---
title: "Import Native Formats to RAVE"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
build_pipeline <- raveio::configure_knitr()
# build_pipeline(make_file = "make-import_lfp_native.R")
if(FALSE){
  settings <- raveio::load_yaml(file.path(rstudioapi::getActiveProject(), "modules", 'import_lfp_native', "settings.yaml"))
  list2env(as.list(settings), envir = environment())
}
```

```{rave obtain_subject_instance, language = "R", export = "subject", format = "rave-subject"}
# raveio::pipeline_debug(quick = FALSE)
subject_id <- sprintf("%s/%s",
                      import_setup__project_name,
                      import_setup__subject_code)

subject <- raveio::RAVESubject$new(
  project_name = import_setup__project_name,
  subject_code = import_setup__subject_code,
  strict = FALSE
)

```

```{rave validate_data, language = "R", export = "validation_result"}

blocks <- import_blocks__session_block
miss_b <- blocks[!blocks%in% subject$preprocess_settings$all_blocks]

if(length(miss_b)) {
  stop("The following block folders are missing: ",
       paste(miss_b, collapse = ", "))
}

electrodes <- dipsaus::parse_svec(import_channels__electrodes)
if(!length(electrodes)) {
  stop("No electrode is set.")
}

sample_rate <- import_channels__sample_rate

if(!length(sample_rate) || !isTRUE(sample_rate > 1)) {
  stop("Sample rate is invalid")
}

format <- import_blocks__format
if(!is.numeric(format)) {
  format <- which(startsWith(names(raveio::IMPORT_FORMATS), trimws(format)))
}

if(isTRUE(skip_validation)) {
  ravedash::logger("`skip_validation` is on.", level = "warn")
  validation_result <- TRUE
} else {
  validation_result <- raveio::validate_raw_file(
    subject_code = subject$subject_code,
    blocks = blocks, electrodes = electrodes,
    format = format
  )
  if(!validation_result) {
    reasons <- attr(validation_result, 'reason')
    if(!is.list(reasons) || !length(reasons)){ stop('rave_import error: unknown reason.') }
    msg <- sapply(seq_along(reasons), function(ii){
      nm <- names(reasons)[[ii]]
      items <- reasons[[ii]]
      paste0(ii, ' - ', nm, '\n', paste0('    ', items, collapse = '\n'))
    })
    stop('The following issues found when validating subject ',
         sQuote(subject$subject_code), ' in project ', sQuote(subject$project_name),
         '.\n', msg, call. = bquote(raveio::validate_raw_file(
      subject_code = .(subject$subject_code),
      blocks = .(blocks), electrodes = .(electrodes),
      format = .(format)
    )))
  }
}

```

```{rave check_import_signals, language = "R", export = "preprocess_info", cue = "always", format = "rave-subject"}

force(validation_result)

# ensure subject path
subject$initialize_paths(include_freesurfer = FALSE)

blocks <- import_blocks__session_block
electrodes <- dipsaus::parse_svec(import_channels__electrodes)
sample_rate <- import_channels__sample_rate
format <- import_blocks__format
if(!is.numeric(format)) {
  format <- which(startsWith(names(raveio::IMPORT_FORMATS), trimws(format)))
}
physical_unit <- import_channels__unit
if(length(physical_unit) != 1 || is.na(physical_unit) ||
   physical_unit == "NA") {
  physical_unit <- NA
} else if (!physical_unit %in% c("V", "mV", "uV")) {
  physical_unit <- NA
}

if(force_import) {
  preproc <- subject$preprocess_settings
  preproc$data$checklevel <- 0L
  
  existing <- preproc$electrodes
  existing <- existing[!existing %in% electrodes]
  preproc$data$electrodes <- NULL
  preproc$data$`@remove`(as.character(electrodes))
  
  if(!setequal(preproc$blocks, blocks)) {
    lapply(existing, function(e){
      preproc$data[[as.character(e)]]$data_imported <- FALSE
    })
    preproc$set_blocks(blocks)
  }
  preproc$set_electrodes(electrodes, type = "LFP", add = TRUE)
  preproc$set_sample_rates(sample_rate, type = "LFP")
  preproc$save()
}

raveio::rave_import(
  project_name = subject$project_name,
  subject_code = subject$subject_code,
  blocks = blocks, electrodes = electrodes,
  sample_rate = sample_rate, format = format,
  conversion = physical_unit,
  data_type = "LFP", add = FALSE, 
  skip_validation = TRUE
)

tryCatch({
  # Save to electrodes.csv
  has_fs <- !is.null(raveio::rave_brain(subject))
  
  # check if electrodes.csv exists
  orig <- subject$get_electrode_table(reference_name = ".fake", simplify = FALSE)
  
  # Try to import
  raveio::import_electrode_table(
    path = file.path(subject$meta_path, "electrodes.csv"),
    subject = subject, use_fs = has_fs)

}, error = function(e){
  ravedash::logger("Cannot import from existing electrodes.csv, creating a new one", level = "warning")
  tbl <- data.frame(
    Electrode = subject$electrodes,
    Coord_x = 0, Coord_y = 0, Coord_z = 0,
    Label = "NoLabel", 
    SignalType = subject$electrode_types
  )
  raveio::save_meta2(
    data = tbl,
    meta_type = "electrodes",
    project_name = subject$project_name,
    subject_code = subject$subject_code
  )
})

module_id <- "import_lfp_native"
subject$set_default(
  namespace = module_id,
  key = "import_parameters",
  value = list(
    project_name = subject$project_name,
    subject_code = subject$subject_code,
    blocks = blocks,
    electrodes = dipsaus::deparse_svec(electrodes),
    sample_rate = sample_rate,
    format = format,
    format_readable = names(raveio::IMPORT_FORMATS)[[format]],
    conversion = physical_unit,
    data_type = "LFP",
    add = FALSE,
    timestamp = strftime(Sys.time(), usetz = TRUE)
  )
)

preprocess_info <- raveio::RAVEPreprocessSettings$new(subject$subject_id, read_only = TRUE)
```



## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-import_lfp_native.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-import_lfp_native.R")
```


Once the pipeline script `make-import_lfp_native.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)


```{r visualize, echo=FALSE}
Sys.setenv("RAVE_PIPELINE" = normalizePath("."))
raveio::pipeline_visualize()
```








