---
title: "RAVE Preprocessing - Morlet Wavelet"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
# This code block sets up the engine environment
# Please do not remove me
raveio::pipeline_setup_rmd(module_id = "wavelet_module")
```

```{rave load_subject, language = "R", export = "subject", cue = "always", format = "rave-subject"}

# check if project and subject are valid
stopifnot(grepl("^[a-zA-Z0-9_]{1,}$", project_name))
stopifnot(grepl("^[a-zA-Z0-9_]{1,}$", subject_code))

subject <- raveio::RAVESubject$new(
  project_name = project_name, 
  subject_code = subject_code
)
print(subject)
```

```{rave clear_cache, language = "R", export = "clear_cache", cue = "always"}
# clear all existing cache data in cache_dir

clear_cache <- raveio::clear_cached_files(
  subject_code = subject$subject_code
)

```

```{rave get_notch_filter_timestamp, language = "R", export = "notch_filtere_stamp", cue = "always"}
notch_filtere_stamp <- subject$get_default(namespace = "notch_filter", "parameters", default_if_missing = Sys.time())
```

```{rave check_prerequisite, language = "R", export = "notch_filtered_electrodes", cue = "always"}
electrodes <- subject$electrodes
etypes <- subject$electrode_types
notch_filtered_electrodes <- electrodes[
  subject$preprocess_settings$notch_filtered &
    etypes %in% c("LFP", "EKG", "Audio")
]
if(!length(notch_filtered_electrodes)) {
  stop("There is no electrode available to the wavelet module")
}
```

```{rave get_raw_sample_rates, language = "R", export = "sample_rates", cue = "always"}
sample_rates <- subject$preprocess_settings$sample_rates
electrodes <- subject$electrodes

sample_rates <- sapply(notch_filtered_electrodes, function(e){
  re <- sample_rates[electrodes == e]
  if(!length(re)) {
    stop("Electrode ", e, " does not have sample rate. The data might not be imported correctly and some configurations are missing.")
  }
  re[[1]]
})

```



```{rave check_kernel, language = "R", export = "kernels", cue = "always"}

freqs <- unlist(kernel_table$Frequency)
cycles <- unlist(kernel_table$Cycles)

if(any(is.na(freqs) | freqs <= 0)) {
  stop("The wavelet kernel table contains negative `Frequency` value(s)")
}

if(length(cycles) != 2) {
  if(length(freqs) != length(cycles)) {
    stop("The wavelet kernel table lengths are inconsistent: the lenth of `Cycles` must be either 2 (a range on which wavelet cycles that will be interpolated log-linearly), or the same length as `Frequency`.")
  }
}

if(any(is.na(cycles) | cycles <= 1)) {
  stop("The wavelet kernel table contains negative or 0 `Cycles` value(s): wavelet cycles must be greater equal than 1 (also integer numbers are strongly recommended)")
}

if(length(freqs) != 2 && length(cycles) == 2) {
  if(cycles[[1]] > cycles[[2]]) {
    stop("The wavelet kernel table: when `Cycles` is a range, (length of 2), it must be in non-decreasing order.")
  }
}

if(length(precision) != 1 || !precision %in% c("float", "double")) {
  precision <- "float"
}

kernels <- list(
  freqs = freqs,
  cycles = cycles,
  precision = precision
)

```


```{rave run_wavelet, language = "R", export = "wavelet_params", cue = "always"}
wavelet_params <- raveio:::run_wavelet(
  subject = subject, electrodes = notch_filtered_electrodes, 
  freqs = kernels$freqs, cycles = kernels$cycles,
  target_sample_rate = target_sample_rate,
  kernels_precision = kernels$precision, 
  pre_downsample = pre_downsample,
  verbose = TRUE
)
```



## Build, Visualize, & Run

Please make sure the following code block is at the end of your pipeline file. This block will build the pipeline and generate a `make-wavelet_module.R` script with your pipeline markdown file. `RAVE` will use the generated pipeline script to execute the pipeline in the dashboard application, or in massive production mode.

```{r build, echo=FALSE, results='hide'}
build_pipeline(make_file = "make-wavelet_module.R")
```


Once the pipeline script `make-wavelet_module.R` is built, you can visualize and execute the pipeline without the need of re-knit this document. Notice we use `r` block instead of `rave`. (This is because the code blocks are not part of pipeline targets.)

```{r visualize, echo=FALSE}
Sys.setenv("RAVE_PIPELINE" = normalizePath("."))
raveio::pipeline_visualize()
```






